The hydra and the rooster

### 2020-08-21 latex/chapter-large-sets.tex
typo corrections in *.tex

>>>>

\index{Projects}
\begin{project}
Instead of considering standard paths and battles, consider ``constant'' paths and the corresponding battles. Please use \texttt{Equations} in order to define the function that computes the length of the $k$-path which leads  from $\alpha$ to $0$.
Prove a few  exact formulas and minoration lemmas.
\end{project}
